Reviewer comments from PeerJ

### 2015-03-06 PeerJResponse.tex
Comments and text, figures
Edits to locus figure. Weird box around it that we need to get rid of
Response edits
Edits to response concerning gel; unable to redo but have edited image
and legend & corresponding text to be more clear

\lev{Okay can do this. maybe will clear up their misunderstanding detailed above}

\lev{changed to be within manuscript. sizes added to figure legend}

@@

\lev{I can relabel or clarify in the figure legend. I don't think that redoing a gel is possible at this point.}

@@

\lev{Redoing gel not possible at this point}

\mbh{even if you have a better resolution image to include, that might help.  I'd also remove the pif lanes as possible as we never mention this}

@@

\lev{We can relabel but not redo gels at this point}
\mbh{the PCR results were conclusive, but I'd make an effort to make the figure more clear with labeling or a higher resolution image and to clarify the description of the banding patterns of the genotypes in the text; my guess is we'll need to do a good job of this in particular if we want this manuscript in \emph{PeerJ}}

>>>>

\res{We have edited this figure to include primer names and added expected amplification sizes to the figure legend.}

@@

\res{We have edited the figure and the figure legend to be more clear.}

@@

\res{It is not feasible for us to redo the gel at this point in time; however, we have editied the figure and the figure legend to be more clear.}

@@

\res{We have editied the figure and the legend and corresponding text reference to be more clear about the expected banding patterns for the 3 genotypes.}
